
\sujet{Computational Geometry and Pattern Recognition}

\noindent
{\bf Duration: 1h30 / 20 points}


NO document, NO internet connection.

\section{Voronoi diagram (4 points)}
\index{Computational Geometry:Voronoi Diagram}

\begin{qbox}
 \begin{enumerate}
  \item Define the Voronoi diagram of a set of points $S\subset\R^n$ and a distance $d$.
  \item Draw a figure to illustrate this diagram. Some specific locations show interesting properties: mention and illustrate them.
  \item Cite and roughly explain the principle of an algorithm that can construct such a diagram. What is its complexity?
  \item Is there a way to develop a complexity in $O(n)$ in order to compute the Voronoi diagram, while $n$ is the number of points of $S$?
  
 \end{enumerate}

\end{qbox}

\section{Delaunay triangulation (4 points)}
\index{Computational Geometry:Delaunay Triangulation}
\begin{qbox}
\begin{enumerate}
 \item What is a triangulation?
 \item For a given point set $S$, is there a unique triangulation?
 \item What is a Delaunay triangulation? Is it unique?
 \item Mention and illustrate the properties of a Delaunay triangulation on a figure.
\end{enumerate}
\end{qbox}

\section{Alpha shapes (3 points)}
\index{Computational Geometry:Alpha Shapes}
\begin{qbox}
 \begin{enumerate}
  \item What is an alpha-shape?
  \item What are the limitations of alpha-shapes?
  \item What are the solutions for such limitations?
 \end{enumerate}

\end{qbox}

\section{Features detectors (9 points)}\index{Features!Detection}
\begin{qbox}
\begin{enumerate}
 \item Mention a few features detectors?
 \item Explain in detail one of them?
 \item Explain the way of performing image registration (panorama reconstruction).
\end{enumerate}
\end{qbox}

